Depression_Vis

### 2023-04-21 Depression_Vis.Rmd
Deleting all of my hard work :(

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL) +
  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
  geom_vline(xintercept = 13, color = "red",alpha =.5)+
  annotate("text", x = 5, y = 34, label = "Q1") +
  annotate("text", x = 8, y = 34, label = "Mean") +
  annotate("text", x = 13, y = 34, label = "Q3")

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")+
  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
  geom_vline(xintercept = 13, color = "red",alpha =.5)+
  annotate("text", x = 5, y = .01, label = "Q1") +
  annotate("text", x = 8, y = .01, label = "Mean") +
  annotate("text", x = 13, y = .01, label = "Q3")

@@

ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  labs(subtitle = "Broken up by Discharge Date")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
  scale_color_manual(values=c("skyblue","#0065A3",
                              "navy","blue"))+
  theme(panel.background=NULL)+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

@@

Example of plot for 1-5 days discharge
```{r}
#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_CUDOS_Race<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF1<-Mothership_Mean_CUDOS_Race[1:34,]
# plot
Race1<-ggplot(data=subset(RaceDF1,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

We are going to make seperate plots for the other duration groups (i.e., 6-10 days,11-15 days, 16+ days)
```{r,include=FALSE}

######## 6-10 days
RaceDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF2<-RaceDF2[1:70,]

# plot
Race2<-ggplot(data=subset(RaceDF2,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

######## 11-15 days
RaceDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF3<-RaceDF3[1:105,]

# plot
Race3<-ggplot(data=subset(RaceDF3,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

######## 16+ days
RaceDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF4<-RaceDF4[1:140,]

# plot
Race4<-ggplot(data=subset(RaceDF4,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

#### putting them all together
```{r}
ggpubr::ggarrange(Race1,Race2,Race3,Race4,ncol=2,nrow=2)
```

@@

Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )
#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF1<-Mothership_Mean_CUDOS_Gender[1:30,]
# plot
Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
GenderDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

GenderDF2<-GenderDF2[1:59,]

# plot
Gender2<-ggplot(data=subset(GenderDF2,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 10-15 Days
GenderDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

GenderDF3<-GenderDF3[1:90,]

# plot
Gender3<-ggplot(data=subset(GenderDF3,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 16+ Days
GenderDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF4<-GenderDF4[1:120,]

# plot
Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
```

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Depression Variable and Track
Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

Break it up by duration group (Treatment track)
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
TrackDF1<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
TrackDF1<-TrackDF1[1:20,]
# plot
Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by Track During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
TrackDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

TrackDF2<-TrackDF2[1:40,]

# plot
Track2<-ggplot(data=subset(TrackDF2,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by Track During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 10-15 Days
TrackDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

TrackDF3<-TrackDF3[1:60,]

# plot
Track3<-ggplot(data=subset(TrackDF3,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by Track During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 16+ Days
TrackDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
TrackDF4<-TrackDF4[1:80,]

# plot
Track4<-ggplot(data=subset(TrackDF4,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by Track During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Depression Variable and Education
Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
EducationDF1<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Education Level During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
EducationDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

EducationDF2<-EducationDF2[1:90,]

# plot
Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Education Level During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 10-15 Days
EducationDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

EducationDF3<-EducationDF3[1:135,]

# plot
Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Education Level During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 16+ Days
EducationDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
EducationDF4<-EducationDF4[1:180,]

# plot
Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by Education Level During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
```
### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Depression Variable and Year
Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

```
```

Break it up by duration group (Year)
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
YEARTXDF1<-Mothership_Long_dep %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
YEARTXDF1<-YEARTXDF1[1:40,]
# plot
YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
YEARTXDF2<-Mothership_Long_dep %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

YEARTXDF2<-YEARTXDF2[1:80,]

# plot
YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 10-15 Days
YEARTXDF3<-Mothership_Long_dep %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

YEARTXDF3<-YEARTXDF3[1:120,]

# plot
YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    #title ="Depression Severity by TX",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 16+ Days
YEARTXDF4<-Mothership_Long_dep %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
YEARTXDF4<-YEARTXDF4[1:180,]

# plot
YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
ggpubr::ggarrange(YEARTX1,YEARTX2,YEARTX3,YEARTX4,ncol=2,nrow=2)
```

>>>>

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL)

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")

@@

ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  labs(subtitle = "Broken up by Discharge Date")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
  scale_color_manual(values=c("skyblue","#0065A3",
                              "navy","blue"))+
  theme(panel.background=NULL)
```

@@

@@

Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )
#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Depression Variable and Track
Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

### EDUCATION
```{r}
#Create a New Data Set with an Average Depression Variable and Education
Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Depression Variable and Year
Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@
